---
title: "Logistic Regression_Abalone"
author: "Sanmoy Paul"
date: "14 April 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Set Working Directory**
```{r setwd, echo=TRUE} 
setwd("C:/F/NMIMS/DataScience/Sem-2/DS/Project")
```

**Load Libraries**
```{r LoadLibraries, echo=TRUE}  
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(gridExtra)
library(plotly)
library(MASS)
library(caTools)
library(ISLR)
library(glmnet)
library(caret)
library(ROCR)
``` 

**Read Csv**
```{r readCSV, echo=TRUE}
AbaloneData<-read.csv("./data/logistic/Abalone.csv", header = TRUE, stringsAsFactors = FALSE)
```   

**Read First 6 recs**
```{r ReadFirst, echo=TRUE}
head(AbaloneData)
```
**Read Last 6 recs**
```{r ReadLast, echo=TRUE}
tail(AbaloneData)
```

**Structure of the data frame**
```{r struc, echo=TRUE}
str(AbaloneData)
glimpse(AbaloneData)
```

**No of Cols**
```{r nCol, echo=TRUE}
ncol(AbaloneData)
```

**No of rows**
```{r nRow, echo=TRUE}
nrow(AbaloneData)
```

**Names**
```{r colNames, echo=TRUE}
names(AbaloneData)
colnames(AbaloneData)
```  

**Summary stat**
```{r summaryStat, echo=TRUE}
summary(AbaloneData)
```  

**Convert into factors**
```{r convertFactors, echo=TRUE}
AbaloneData$sex<-ifelse(AbaloneData$sex=='M', 1, 0)
AbaloneData$sex<-as.factor(AbaloneData$sex)

```

**Detect NAs**
```{r detectNAs, echo=TRUE}
detectNAs<-function(x){
  return(sum(is.na(x)))
}
lapply(AbaloneData, detectNAs)
```


**Split into Train and Test Set**
```{r splitting, echo=TRUE}
set.seed(100)
split<-sample.split(AbaloneData$sex, SplitRatio=0.8)
trainSet<-subset(AbaloneData, split==TRUE)
testSet<-subset(AbaloneData, split==FALSE)
```


**Train Model_1**
```{r trainModel1, echo=TRUE}
log.fit1 <- glm(sex ~ ., data=trainSet, family = "binomial")
summary(log.fit1)
```

**Train Model_2**
```{r trainModel2, echo=TRUE}
log.fit2 <- glm(sex ~ (length+diameter+weight.w+weight.s+weight.v+weight.sh+rings), data=trainSet, family = "binomial")
summary(log.fit2)
```

**Train Model_3**
```{r trainModel3, echo=TRUE}
log.fit3 <- glm(sex ~ (length+diameter+weight.s+weight.v+weight.sh+rings), data=trainSet, family = "binomial")
summary(log.fit3)
```

**Train Model_4**
```{r trainModel4, echo=TRUE}
log.fit4 <- glm(sex ~ (length+weight.s+weight.v+weight.sh+rings), data=trainSet, family = "binomial")
summary(log.fit4)

```

**Train Model_5**
```{r trainModel5, echo=TRUE}
log.fit5 <- glm(sex ~ (weight.s+weight.v+weight.sh+rings), data=trainSet, family = "binomial")
summary(log.fit5)
```

**Train Model_6**
```{r trainModel6, echo=TRUE}
log.fit6 <- glm(sex ~ (weight.s+weight.sh+rings), data=trainSet, family = "binomial")
summary(log.fit6)

```

**Predict Model**
```{r predictModel, echo=TRUE}
predict.fit<-predict(log.fit6, newdata = testSet, type="response")
```

**Confusion Matrix**
```{r confMatrix, echo=TRUE}
conf_ablone<-table(predicts=predict.fit>0.5, actuals=testSet$sex)
conf_ablone
```

**Accuracy**
```{r accuracy, echo=TRUE}
accuracy_ablone=sum(diag(conf_ablone))/sum(conf_ablone)
accuracy_ablone
```

**Precision**
```{r precision, echo=TRUE}
precision=(469)/(469+257)
precision
```

**Recall**
```{r recall, echo=TRUE}
recall=(469)/(469+61)
recall
```

**ROCR Curve**
```{r rocrCurve, echo=TRUE}
ROCRpred <- prediction(predict.fit, testSet$sex)
ROCRperf <- performance(ROCRpred, 'tpr','fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2,1.7))
auc.tmp <- performance(ROCRpred,"auc")
auc <- as.numeric(auc.tmp@y.values)
auc
```
**Predictions Results**
```{r predictions, echo=TRUE}
pred <- ifelse(predict.fit >= 0.5, "Male", "Female") 
pred
```
